% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\textbf{Introduction to Digital Design -- EENG284}

\textbf{Spring 2024}

\textbf{Dr. Chris Coulston, Associate Teaching Professor, 303.273.3265,
coulston@mines.edu}

\textbf{Office: BB 310F (Brown Hall)}

\textbf{Office hours: MWF 1:30 -- 3:00}

\textbf{Course Title: Digital Logic}

\textbf{Course Meeting:} Lecture MW F 9:00-9:50 130 Coors Tek Chris
Coulston

Lab A T 8:00-10:50 305 Brown

Lab B T 11:00-1:50 305 Brown

Lab C T 2:00-4:50 305 Brown

Lab D T 5:00-7:50 305 Brown

\textbf{Course Description:} Fundamentals of digital logic design.
Covers combinational and sequential logic circuits, programmable logic
devices, hardware description languages, and computer-aided design (CAD)
tools. The emphasis is to design complex logic circuits using a datapath
and control approach. The laboratory component introduces design,
simulation and synthesis of designs on an FPGA.

\textbf{Prerequisite: CSCI 261}

\textbf{Co-requisite: EENG 281, or EENG 282, or PHGN 215}

\textbf{Textbook(s):} Free: Digital Design: A datapath and control
approach

\textbf{Course Objectives:}

\begin{itemize}
\item
  Convert between numbering representations,
\item
  Design a combinational logic circuit from a word statement to a
  circuit diagram,
\item
  Manipulate a logic function in any of its representations; word
  statement, truth table, symbolic, and circuit diagram,
\item
  Determine SOPmin and POSmin realizations of logic function with or
  without don\textquotesingle t cares,
\item
  Build and operate adders, comparators, multiplexers and decoders,
\item
  Determine output behavior of D,T,SR,JK; latches, clock latches and
  flip flops,
\item
  Build and operate registers, shift registers, counters, tri-state
  logic and RAMs,
\item
  Design Finite State Machines using a dense or Ones Hot encoding,
\item
  Implement complex digital systems using the datapath and control
  design approach.
\end{itemize}

\textbf{\hfill\break
Topics Covered:} This is an approximate timeline; changes may be made
through the semester.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0816}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1239}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.5109}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1418}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1418}}@{}}
\toprule()
\endhead
Session & Date & Topic & Assignment & Reading \\
No Lab & Jan 9 & No Lab & & \\
1 & Jan 10 & Course Intro, Binary numbering, Hexadecimal & & 1.1 --
1.3 \\
2 & Jan 12 & Binary Addition & & 1.4 \\
& Jan 15 (M) & Martin Luther King Day & & \\
No Lab & Jan 16 & Snow Day -- Classes Canceled & & \\
3 & Jan 17 & Logic gates / Circuit to Symbolic / Circuit to Truth Table
& & 2.1, 2.21, 2.2.2 \\
4 & Jan 19 & Symbolic to Truth Table / Symbolic to Circuit & HW\#1 Due &
2.2.3, 2.2.4 \\
5 & Jan 22 (M) & Symbolic to Verilog & & Supplemental \\
Lab \#1 & Jan 23 & Introduction to CAD tools and Verilog & & \\
6 & Jan 24 & Symbolic to Symbolic & & 2.2.5 \\
7 & Jan 26 & Symbolic to Symbolic & & 2.2.5 \\
8 & Jan 29 (M) & Truth Table to Symbolic SOP and POS & HW\#2 Due &
2.2.6, 2.2.7, 2.3 \\
& Jan 30 & Career Fair & & \\
& Jan 31 & Career Fair & & \\
9 & Feb 2 & Karnaugh Maps, 3 variables & & 3.1 \\
10 & Feb 5 (M) & Combinational Logic with Verilog & & Supplemental \\
Lab \#2 & Feb 6 & Hexadecimal to 7-segment Converter & Lab \#1 Due & \\
11 & Feb 7 & Karnaugh Maps, 4 and 5 variables & HW\#3 Due & 3.2, 3.3 \\
12 & Feb 9 & Don't cares & & 3.5 \\
& Feb 12 (M) & SOP and POS in Karnaugh maps & & \\
& Feb 13 & Rock Paper Scissors & Lab \#2 Due & \\
13 & Feb 14 & Exam Review & HW\#4 Due & 3.6 \\
& Feb 16 & Exam I & & \\
14 & Feb 19 (M) & Presidents' Day & & 4.1 \\
Lab \#3 & Feb 20 & Presidents' Day & & \\
15 & Feb 21 & Decoder / Multiplexers & & 4.2 \\
16 & Feb 23 & 2's complement & & 1.5 \\
17 & Feb 26 (M) & Adders & HW\#5 Due & 4.3 \\
Lab \#4 & Feb 27 & Guessing Game & Lab \#3 Due & \\
18 & Feb 28 & Adder Subtractor & & 4.4 \\
19 & March 1 & Comparator & & 4.5 \\
20 & March 4 (M) & Wire Logic / Combinations & & 4.7, 4.8 \\
Lab \#5 & March 5 & Guessing Game with Hints & Lab \#4 Due & \\
21 & March 6 & SR Latch & HW\#6 Due & 5.5 \\
22 & March 8 & Basic memory elements -- timing & & 5.1 \\
23 & March 11 (M) & Basic memory elements -- practical considerations &
& 5.7 \\
Lab \#6 & March 12 & Decimal Calculator & Lab \#5 Due & \\
24 & March 13 & Register & HW\#7 Due & 6.1 \\
25 & March 15 & Shift Registers & & 6.2 \\
& March 18 (M) & Spring Break & & \\
26 & March 25 (M) & Counter & & 6.3 \\
Lab \#7 & March 26 & 1 Dimensional Cellular Automata & Lab \#6 Due &
6.3 \\
27 & March 27 & RAM & & 6.4 \\
28 & March 29 & Register Transfer & & 6.5 \\
& April 1 (M) & Exam Review & HW\#8 Due & Supplemental \\
Lab \#8 & April 2 & Mod 10 Counter & Lab \#7 Due & \\
& April 3 & Exam II & & \\
29 & April 5 & Sequential Design -- Traffic Light Controller & & 7.4 \\
30 & April 8 (M) & Sequential Design -- Verilog & & Supplemental \\
Lab \#9 & April 9 & Stopwatch Datapath & Lab \#8 Due & \\
31 & April 10 & Sequential Design -- Timing & & 7.6 \\
& April 11-12 & E Days & & 7.4 \\
32 & April 15 (M) & Sequential Design -- Vending Machine & HW\#9 Due &
7.5 \\
Lab\#10 & April 16 & Stopwatch Control & Lab \#9 Due & \\
33 & April 17 & Datapath and Control Theory & & 8.1, 8.2, 8.3 \\
37 & April 19 & Datapath and Control Theory & & 8.1, 8.2, 8.3 \\
38 & April 22 (M) & Datapath and Control Practice & HW\#10 Due & 8.4,
8.5 \\
Lab\#11 & April 23 & Stopwatch -- Datapath and Control & Lab \#10 & \\
39 & April 24 & Datapath and Control Practice & & 8.4, 8.5 \\
40 & April 26 & Datapath and Control Timing & & 8.4, 8.5 \\
41 & April 29 (M) & Datapath and Control Practice & & 8.7 \\
& April 30 & Turn in Stopwatch & Lab \#11 Due & \\
42 & May 1 & Exam Review & HW\#11 Due & Supplemental \\
& May 6 & Exam III at 3:15pm in 130 Coors Tek & & \\
\bottomrule()
\end{longtable}

\textbf{Homework:} I will assume that your homework solutions represent
individual effort. This point deserves some attention. At what point
does working together become copying? \emph{I encourage students to help
one another, but you must keep working on independent solutions.}
Don\textquotesingle t arrive at a solution with a friend then both copy
that solution. If two solutions are identical then I will assume that
one was copied from another. Please do not go down this road.

Suggest format for homework.

\begin{itemize}
\item
  Complete your work on green engineering paper,
\item
  Format the top of the first sheet as follows using the 5 cells at the
  top of the green engineering paper. This example assumes your homework
  1 solutions require 4 pages.
\end{itemize}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2007}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2009}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2014}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2006}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1964}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
HW\#1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
EENG 284
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textless Your name\textgreater{}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textless Due Date\textgreater{}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
1/4
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{itemize}
\item
  You should format all subsequent pages as follows:
\end{itemize}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2025}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1972}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2032}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1972}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1999}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
HW\#1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textless Your name\textgreater{}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
2/4
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

When you complete your homework, it needs to be turned in on Canvas
using the following procedure.

\begin{itemize}
\item
  Make a clear scan of each page,
\item
  Combine all pages into a single PDF document,
\item
  Upload PDF to Canvas before 11:59pm on the due date.
\end{itemize}

I will assess a 50\% penalty per calendar day for late homework. I will
not grant extensions to the homework due dates under any circumstances.
I will drop your lowest 2 homework scores.

\textbf{Lab:} We will meet weekly in 305 Brown Hall. You will be able to
complete many of the labs during the 3-hour lab session. However, some
labs may require more time and may need to be worked on outside lab
times. In these cases, you will have access to the hardware. You may use
lab stations outside of our class if they are not being used by another
scheduled class. It's always a good idea to ask one of the lab
instructors if it's OK to work in the lab. Labs should be completed and
turn-in a week later at the beginning of your lab session. Late
assignments (labs and inLabs) are assessed a 50\% late penalty per
calendar day.

\textbf{Exams:}

\begin{itemize}
\item
  Exams will be administrated online using Canvas,
\item
  Exams will be scheduled during the class meeting time,
\item
  Some exam questions may require you to upload photos showing your
  work,
\item
  You may take the exam wherever you feel comfortable,
\item
  The academic integrity guidelines apply while you are taking the exam.
\end{itemize}

\textbf{Makeup Exams:} You can arrange makeup exams for prior
commitments (i.e. wedding or sporting event) or an emergency. Prior
arrangements are appreciated but, in an emergency, (an unforeseen
circumstance that poses immediate risk to health, life property or the
environment), please take care of the emergency first. As soon as
possible:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Contact me at my office phone (303.273.3265), or
\item
  Contact me by email (coulston@mines.edu).
\end{enumerate}

Contact me as soon as you are able to return to campus. In general, I am
understanding about makeup exams -- I do not want anyone hurt attempting
to make it to campus as a result of foul weather. Please show me the
same respect and honesty as you would like me to show you and everything
will be fine.

\textbf{Grades:} The grade you earn in this class will based on the
following distribution of points:

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.6672}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3328}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Exam 1
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
15\%
\end{minipage} \\
\midrule()
\endhead
Exam 2 & 15\% \\
Labs & 30\% \\
Final Exam & 20\% \\
Homework & 20\% \\
\bottomrule()
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3366}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3317}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3317}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Grade
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Lower
\end{minipage} \\
\midrule()
\endhead
A & 100 & 93+ \\
A- & 93- & 90+ \\
B+ & 90- & 87+ \\
B & 87- & 83+ \\
B- & 83- & 80+ \\
C+ & 80- & 77+ \\
C & 77- & 73+ \\
C- & 73- & 70+ \\
D+ & 70- & 63+ \\
D & 67- & 63+ \\
D- & 63- & 60+ \\
F & 60- & 0.0 \\
\bottomrule()
\end{longtable}

\textbf{Office Hours:} I like to pile everyone in my office during
office hours. What this means is I generally like to have everybody in
the office asking questions. In this way, many problems can be addressed
at once. Since I teach multiple classes, there may be students from a
different class all piled in my office. If this is the case, please
interrupt me and let me know that you have a question from a different
class. I will let the students present know that I need to attend to a
question from another class and give them and give them 10 minutes to
wrap-up their questions before I switch to yours.

\textbf{Academic Integrity:} The Colorado School of Mines affirms the
principle that all individuals associated with the Mines academic
community have a responsibility for establishing, maintaining and
fostering an understanding and appreciation for academic integrity. In
broad terms, this implies protecting the environment of mutual trust
within which scholarly exchange occurs, supporting the ability of the
faculty to fairly and effectively evaluate every student's academic
achievements, and giving credence to the university's educational
mission, its scholarly objectives and the substance of the degrees it
awards. The protection of academic integrity requires there to be clear
and consistent standards, as well as confrontation and sanctions when
individuals violate those standards. The Colorado School of Mines
desires an environment free of any and all forms of academic misconduct
and expects students to act with integrity at all times. Academic
misconduct is the intentional act of fraud, in which an individual seeks
to claim credit for the work and efforts of another without
authorization, or uses unauthorized materials or fabricated information
in any academic exercise. Student Academic Misconduct arises when a
student violates the principle of academic integrity. Such behavior
erodes mutual trust, distorts the fair evaluation of academic
achievements, violates the ethical code of behavior upon which education
and scholarship rest, and undermines the credibility of the university.
Because of the serious institutional and individual ramifications,
student misconduct arising from violations of academic integrity is not
tolerated at Mines. If a student is found to have engaged in such
misconduct sanctions such as change of a grade, loss of institutional
privileges, or academic suspension or dismissal may be imposed. For this
course, the following rules should be followed.

\begin{itemize}
\item
  Copying of solutions without understanding them is not allowed; if a
  student copies a solution and cannot explain it adequately this is
  considered academic dishonesty.
\item
  During quizzes and exams, students must do 100 percent of the work on
  their own.
\item
  The nominal penalty for academic dishonesty is an 'F' in the course.
\end{itemize}

\textbf{Disability Support Statement:}

The Colorado School of Mines is committed to ensuring the full
participation of all students in its programs, including students with
disabilities. If you are registered with Disability Support Services
(DSS) and I have received your letter of accommodations, please contact
me at your earliest convenience so we can discuss your needs in this
course. For questions or other inquiries regarding disabilities, I
encourage you to visit disabilities.mines.edu for more information.

\textbf{Absenteeism (from Undergraduate Bulletin)}

Class attendance is required of all undergraduates unless the student
has an official excused absence. Excused absences are granted for three
general reasons:

\begin{quote}
1. Student is a varsity athlete and is representing the School in a
varsity athletics activity.

2. Student is representing the School in an authorized activity related
to a club or academic endeavor (academic competitions, student
professional society conferences, club sport competition,
program-sponsored competitions, etc.)

3. Student has a documented personal reason (illness, injury, jury duty,
life-threatening illness or death in the immediate family, military
service, etc.).
\end{quote}

Students who miss academic work (including but not limited to exams,
homework, and labs) for one of the reasons listed above may be issued an
excused absence. If an excused absence is received, the student must be
given the opportunity to make up the missed work in a reasonable period
of time without penalty. While the student is not responsible for
actually issuing the excused absence, the student is responsible for
making sure documentation is submitted appropriately and for contacting
his/her faculty member(s) to initiate arrangements for making up any
missed work.

\end{document}
