
%%%%%%%%%%%%%%%%%%%%%  Lab #2

You are to design a circuit which control the water pump of
a washing machine.

The pump will not pump water if
\begin{description}
\item The lid is closed and the cycle is not fill
\item The cycle is fill and the detergent level is empty
\item The detergent if not empty and the lid is open
\end{description}

The variable for this problem are
\begin{description}
\item L = lid is closed
\item C = cycle is fill
\item D = detergent is empty
\item P = pump will pump water
\end{description}

Create a truth table which describes when the pump will not
pump water.  Call this output P'.  Determine the canonical SOP 
expression for P'.  Use this canonical SOP expression to generate 
a circuit diagram for P.  This can be done by inserting an 
inverter onto the output of the circuit.

Take the P' column from truth table and invert all the entries
to generate a new output column of the kmap called P (becuase
the negation of P' is P).  Determine the canonical SOP 
realization for P using this new column.

%%%%%%%%%%%%%%%%%%%%%  Lab #3
%% This is just the majority circuit in chapter 2


%%%%%%%%%%%%%%%%%%%%%  Lab #4

Sometimes a logic circuit needs to output a logic 0 in order to
produce some behavior.  For example, you can attach an LED to
a digital circuit output so that it lights up when the circuit 
outputs a 0.  This is called an active low output, the output
device is {\it active} then the digital output is {\it low}.

Build a digital circuit that takes as input 2 2-bit numbers,
A and B.  The circuit has three outputs which drive three
LEDS labeled G, L, and E.  
The G LED should be illuminated when A>B.
The L LED should be illuminated when A<B.
The E LED should be illuminated when A=B.
The LEDs are illuniated when the circuit outputs a 0, otherwise
they are turned off.

Determine \SOPmin expression for the G,L and E outputs.
Determine \POSmin expression for the G,L and E outputs.

%%%%%%%%%%%%%%%%%%%%%  Lab #5
%% Add sub is covered in chapter 4

%%%%%%%%%%%%%%%%%%%%%  Lab #6
%% ALU uses tristate buffer mux
%% shuold move this unit from chapter 6 to chapter 4
%% and move the associated HW questions.


%%%%%%%%%%%%%%%%%%%%%  Lab #7
%% VHDL

%%%%%%%%%%%%%%%%%%%%%  Lab #8
%% serial add/sub


